---
title: "02_Assignment_Barletta"
output: html_document
---

```{r  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(Metrics)
```

```{r data}
load("pd.Rdata")
```

The codebook for this dataset is stored as another dataset, `labels_explain`. The first column in this dataset is variable names, the second column is a full explanation of that variable. 

```{r explain_date}

## Full explanation of data in codebook
load("pd_lab_explain.Rdata")

#or use View
#View(lab_explain)
```



#PROBLEM SET 2 

#QUESTION 1 - CALCULATE THE MEAN OF THE OUTCOME

```{r}
pd%>%summarize(mean_homeown_rate=mean(homeown_rate,na.rm=TRUE))
```

#QUESTION 2 - CREATE A NEW VARIABLE THAT CONSISTS OF THE MEAN OF THE OUTCOME
```{r}
pd<-pd%>%mutate(mean_homeown_rate=mean(homeown_rate,na.rm=TRUE))
```

#QUESTION 3 - CALCULATE A SUMMARY MEASURE OF THE ERRORS FOR EACH OBSERVATION

```{r error_terms}
pd<-pd%>%mutate(e2=homeown_rate-mean_homeown_rate)
```

```{r}
rmse_uncond_mean<-rmse(pd$homeown_rate,pd$mean_homeown_rate)
rmse_uncond_mean
```

#QUESTION 4 - CALCULATE THE MEAN OF THE OUTCOME AT LEVELS OF A PREDICTOR VARIABLE

#ATTEMPT NUMBER ONE 

```{r}
pd%>%group_by(median_hh_inc)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  summarise(homeown_rate=mean(median_hh_inc))

gg<-ggplot(data=pd,aes(x=homeown_rate,y=median_hh_inc,color="Actual"))
gg<-gg+geom_point(alpha=.5,size=.5)
gg<-gg+geom_point(aes(x=homeown_rate,y=median_hh_inc,color="Predicted:Conditional Mean, 1 var"))
gg<-gg+ scale_color_manual("Type",values=c("Predicted:Conditional Mean, 1 var"="red","Actual"="black"))
gg<-gg+theme(legend.position="bottom")
gg<-gg+xlab("Homeownership Rate")+ylab("Median Household Income")
gg

##Save for later
gg3<-gg

```
#ATTEMPT NUMBER TWO 

```{r simple_plots}
## Create a rank variable for homeownership rates 
pd<-pd%>%mutate(homeown_rate=rank(homeown_rate))
```

```{r}
## Plot by rank
gg<-ggplot(data=pd, aes(x=homeown_rate,
                         y=median_hh_inc,
                         text=county))
```

Now I need to declare the type of graphic, or geometry. By specifiying `geom_point` I'm saying I want a scatterplot.
```{r}
## Add Points
gg<-gg+geom_point(alpha=.5,size=.5)
```

Now I'm going to add labels for the x and y axis. 
```{r}
## Add labels
gg<-gg+xlab("Homeownership Rate")+ylab("Median Household Income")
```


And now we're ready to call the graphics object, `gg`
```{r}
gg
```

I'm going to store this `gg` object in another object called `gg1`. This is so I can come back to it later. 
```{r}
gg1<-gg
```

```{r}
# Make Interactive plot
gg_p<-ggplotly(gg)

gg_p
```

#QUESTION 5 - Use these conditional means as a prediction: for every county, use the conditional mean to provide a ‘’best guess” as to that county’s level of the outcome.

#in other words: use the conditional mean as a best guess at that county's level of homeownership

#My predictions are that counties in the 1st quartile will have ownership 

Our notation for this predictor will be:

$$\hat{Y}=(\bar{Y}|X=x) $$

That is, the predicted value of y, $\bar{Y}$ is equal to the mean value of $Y$ given our predictor $X$ (college graduate levels in this case) is equal to a given value of $X$, denoted by $x$. 

Let's see what happened to our RMSE when we did a conditional as opposed to an unconditional mean. 
```{r}
rmse_cond_mean_one<-rmse(pd$percapinc.2010,pd$pred_income_college)
rmse_cond_mean_one
```


*Quick Exercise: Calculate per capita income as a function of the proportion of the county with a high school education*

We can continue "binning" the data to define averages by more and more subgroups. For instance, we might want to calculate the average income by education AND home ownership rate.

## New Variable Home Ownership Rate
```{r}
## Create a variable for quartiles of college education
pd<-pd%>%mutate(coll_grad_pc=ntile(homeown_rate,4))
```

```{r}
pd%>%group_by(coll_grad_pc)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  summarise(pred_income_college=mean(pred_income_college))
```

```{r}
## Create a variable for quartiles of college education
pd<-pd%>%mutate(homeown_rate_level=ntile(homeown_rate,4))
```

```{r}
pd%>%group_by(homeown_rate_level)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  summarise(pred_income_homeown_rate=mean(percapinc.2010))
```


```{r}
pd<-pd%>%group_by(coll_grad_level,homeown_rate_level)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  mutate(pred_income_coll_and_homeown=mean(percapinc.2010))%>% 
  ## Ungroup
  ungroup()%>% 
  #Rank by prediction, with ties sorted randomly
  mutate(pred_income_coll_and_homeown_rank=rank(pred_income_coll_and_homeown,
                                                ties.method="random"))
```

```{r}
rmse_cond_mean_two<-rmse(pd$percapinc.2010,pd$pred_income_coll_and_homeown)
rmse_cond_mean_two
```

```{r}
## Create a variable for quartiles of college education
pd<-pd%>%mutate(homeown_rate_level=ntile(homeown_rate,4))
```

```{r}
pd<-pd%>%group_by(coll_grad_level,homeown_rate_level)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  mutate(pred_income_college_and_homeown=mean(percapinc.2010))%>% 
  ## Ungroup
  ungroup()%>% 
  #Rank by prediction, with ties sorted randomly
  mutate(pred_income_college_and_homeown_rank=rank(pred_income_college_and_homeown,ties.method="random"))
```
  
```{r}
pd%>%group_by(homeown_rate_level)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  summarise(pred_income_homeown_rate=mean(percapinc.2010))
```
```{r}
rmse_cond_mean_two<-rmse(pd$percapinc.2010,pd$pred_income_coll_and_homeown)
rmse_cond_mean_two
```
```{r}
pd%>%group_by(college_grad_level)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  summarise(pred_income_college=mean(percapinc.2010))
```




#5 USE THESE CONDITIONAL MEANS AS A PREDICTION: FOR EVERY COUNTY, USE CONDITIONAL MEANS TO PROVIDE A 'BEST GUESS' AS TO THAT COUNTY'S LEVEL OF THE OUTCOME.

#6 CALCULATE A SUMMARY MEASURE OF THE ERROR IN YOUR PREDICTIONS