---
title: "02_Assignment_Barletta"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r  include=TRUE, warnings=TRUE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(Metrics)
```

```{r data}
load("pd.Rdata")
```

#QUESTION 1 - CALCULATE THE MEAN OF THE OUTCOME

```{r}
pd%>%summarize(mean_homeown_rate=mean(homeown_rate,na.rm=TRUE))
```

#QUESTION 2 - CREATE A NEW VARIABLE THAT CONSISTS OF THE MEAN OF THE OUTCOME
```{r}
pd<-pd%>%mutate(mean_homeown_rate=mean(homeown_rate,na.rm=TRUE))
```

#QUESTION 3 - CALCULATE A SUMMARY MEASURE OF THE ERRORS FOR EACH OBSERVATION

```{r error_terms}
pd<-pd%>%mutate(e2=homeown_rate-mean_homeown_rate)
```

```{r}
rmse_uncond_mean<-rmse(pd$homeown_rate,pd$mean_homeown_rate)
rmse_uncond_mean
```

#QUESTION 4 - CALCULATE THE MEAN OF THE OUTCOME AT LEVELS OF A PREDICTOR VARIABLE

#ATTEMPT NUMBER ONE 

```{r}
pd<-pd%>%mutate(personhhlevel=ntile(person_per_hh,4))
pd%>%select(county,personhhlevel,person_per_hh)%>%View()
table(pd$personhhlevel)
```

```{r}
pd%>%group_by(median_hh_inc)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  summarise(homeown_rate=mean(median_hh_inc))

gg<-ggplot(data=pd,aes(x=homeown_rate,y=median_hh_inc,color="Actual"))
gg<-gg+geom_point(alpha=.5,size=.5)
gg<-gg+geom_point(aes(x=homeown_rate,y=median_hh_inc,color="Predicted:Conditional Mean, 1 var"))
gg<-gg+ scale_color_manual("Type",values=c("Predicted:Conditional Mean, 1 var"="red","Actual"="black"))
gg<-gg+theme(legend.position="bottom")
gg<-gg+xlab("Homeownership Rate")+ylab("Median Household Income")
gg

##Save for later
gg3<-gg

```
#ATTEMPT NUMBER TWO 

```{r simple_plots}
## Create a rank variable for homeownership rates 
pd<-pd%>%mutate(homeown_rate=rank(homeown_rate))
```

```{r}
## Plot by rank
gg<-ggplot(data=pd, aes(x=homeown_rate,
                         y=median_hh_inc,
                         text=county))
```

Now I need to declare the type of graphic, or geometry. By specifiying `geom_point` I'm saying I want a scatterplot.
```{r}
## Add Points
gg<-gg+geom_point(alpha=.5,size=.5)
```

Now I'm going to add labels for the x and y axis. 
```{r}
## Add labels
gg<-gg+xlab("Homeownership Rate")+ylab("Median Household Income")
```


And now we're ready to call the graphics object, `gg`
```{r}
gg
```

I'm going to store this `gg` object in another object called `gg1`. This is so I can come back to it later. 
```{r}
gg1<-gg
```

```{r}
# Make Interactive plot
gg_p<-ggplotly(gg)

gg_p
```

#5 QUESTION 5: USE THESE CONDITIONAL MEANS AS A PREDICTION 

```{r}

##pd<-pd%>%mutate(coll_grad_level=ntile(coll_grad_pc,4))

pd<-pd%>%group_by(personhhlevel)%>% ## Group by predictor
  ##Calculate mean at each level of predictor
  mutate(pred_personhhlevel=mean(percapinc.2010))%>%
  ## Ungroup
  ungroup()%>% 
  #Rank by prediction, with ties sorted randomly
  mutate(pred_personhhlevel_rank=rank(pred_personhhlevel,ties.method="random"))

pd%>%select(county,person_per_hh,personhhlevel,pred_personhhlevel)%>%View()

```

# QUESTION 6 CALCULATE A SUMMARY MEASURE OF THE ERROR IN YOUR PREDICTIONS 

```{r}
rmse_cond_mean_two<-rmse(pd$person_per_hh,pd$pred_personhhlevel)
rmse_cond_mean_two
```
