---
title: "05_06_Assignment_Barletta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#first let's load our libraries 

```{r,echo=FALSE}
rm(list=ls())
library(tidyverse)
library(forcats)
library(ModelMetrics)
library(modelr)
library(ggplot2)
```

#now let's load in the data 

```{r}
load("~/Documents/8200/Scripts and Data Sets/els_train.Rdata")
```

#Let's create a historgram, for the sake of interest!

```{r}
els_train%>%summarize(mean(bynels2m,na.rm=TRUE))

gg<-ggplot(els_train,aes(x=bynels2m))
gg<-gg+geom_histogram()
gg
```
#QUESTIONS 1,3, and 4 - 

#1 - Choose a dependent variable and plot that dependent variable as a function of a contnuous independent variable

#3 - Add a line of best fit to your graphic 

#4 - Clean up the labeling and description of the graphic 

##I am going to look at Reading Scores by SES

```{r}

mod1<-lm(bynels2r~byses1,data=els_train) #outcome on left, predictor on right 

summary(mod1)
confint(mod1)

g1<-ggplot(els_train, aes(x=byses1,y=bynels2r))+ #specify data and x and y
           geom_point(shape=1)+ #specify points
           geom_smooth(method=lm)+ #ask for lm line - this overlays the linear model on a scatterplot
xlab("Socioeconomic Status")+
ylab("Reading Score")+    
ggtitle("Reading Scores",subtitle= "by Socioeconomic Status")
  
g1

#the following adds predictions back to the data frame - use this for question 4

els_train<-els_train%>%add_predictions(mod1)%>%rename(pred1=pred) #predict using data in memory
 
## RMSE
rmse_1<-modelr::rmse(mod1,els_train);rmse_1

#Question

```
#Question 5 - include a few sentences describing what the graphic shows 

```{r}
g1<-g1+geom_smooth(method="lm")
g1<-g1+ylab("Reading Scores")+xlab("Socio Economic Status")
g1
```
```{r}
g1<-g1+geom_smooth(method="loess", color="red")
g1<-g1+ylab("Reading Scores")+xlab("Socio Economic Status")
g1
```

#Questions 6 and 7 

#6 - Create a regression that predicts reading scores as a function of SES plus one other covariate, using the training data. 

##I chose to examine reading score by SES and Math Scores

#7 - Report the RMSE from a validation fo your model using the testing data 

## The RMSE is 8.561206

```{r}

mod2<-lm(bynels2r~byses1+bynels2m,data=els_train) #outcome on left, predictor on right 

summary(mod1)
confint(mod1)

g2<-ggplot(els_train, aes(x=byses1,y=bynels2r))+ #specify data and x and y
           geom_point(shape=1)+ #specify points
           geom_smooth(method=lm)+ #ask for lm line - this overlays the linear model on a scatterplot
xlab("Socioeconomic Status and Math Scores")+
ylab("Reading Score")+    
ggtitle("Reading Scores",subtitle= "by Socioeconomic Status and Math Scores")
  
#the following adds predictions back to the data frame - use this for question 4

els_train<-els_train%>%add_predictions(mod1)%>%rename(pred1=pred) #predict using data in memory
 
## RMSE
rmse_1<-modelr::rmse(mod1,els_train);rmse_1

```

```{r}
g2<-ggplot

## Let's make the dots smaller for readability
g2<-g2+geom_point(size=.25)

```