---
title: "12_Assignment_Barletta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries and Set Knit
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, results ='hide',include=TRUE,messages=FALSE)

library(tidyverse)
library(stats)
library(flexclust)
library(ggplot2)
library(LICORS)
library(knitr)
library(modelr)
```

# QUESTION 1 - DOWNLOAD DATA SET FROM THE WEBSITE AND LOAD INTO R STUDIO 

```{r load_data,results="asis"}
library(readxl)
ev<-read_xlsx("/Users/kimberlybarletta/Documents/8200/GitHub/LLO8200/turkiyestudentevaluation_generic.xlsx")
```

# QUESTION 2 - SELECT 10 VARIABLES TO SERVE AS BASIS FOR CLUSTERING 

```{r kmeans}
c_test <- stepFlexclust(ev, k = 2:7, nrep = 20)
c_test
plot(c_test)
```

#QUESTION 3 - RUN KMEANS APP
```{r kmeans}
cQ3 <- kmeanspp(ev, k = 3, start = "random", iter.max = 1000, nstart = 50)
table(cQ3$cluster)
```

```{r kmeans}
ev_km <-ev
Clusters <- kmeans(ev_km, 4)
ev_km$Clusters <- as.factor(Clusters$cluster)
str(Clusters)
Clusters$centers
```

#QUESTION 4 - SUMMARIZE THE CLUSTERS 
```{r kmeans}
var.means <- colMeans(ev)
var.means <- var.means[-(length(var.means))]
ev_km2 <- ev
ev_km2$Clusters <- as.factor(Clusters$cluster)

sum1 <- ev_km %>% group_by(Clusters) %>% summarize_all(funs(mean), na.rm = TRUE)
sum1

sum2 <- gather(sum1,-'Clusters', key = variable, value = value)
sum2

sum_total <- ev %>% summarize_all(funs(mean))

sum_total <- gather(sum_total, key = variable, value = overall_mean)
sum2 <- left_join(sum2, sum_total, by = "variable")
sum2 <- sum2 %>% group_by(variable) %>% mutate(varmeans = mean(value))

variable_labels <- rev(c(  
  "repeat",
  "attendance",
  "difficulty",
  "Q4",
  "Q7",
  "Q8",
  "Q14",
  "Q19",
  "Q24",
  "Q28"
))

g1 <- ggplot(data = sum2, aes(y = value, x = variable, fill = variable))
g1 <- g1 + geom_bar(stat = "identity") + coord_flip() + theme(legend.position = "none")
g1 <- g1 + scale_x_discrete(labels = variable_labels)
g1 <- g1 + geom_point(data = sum2, aes(y = overall_mean, x = variable))
g1 <- g1 + facet_wrap(~Clusters)
g1

```

# QUESTION 5 - TRY RUNNING A HAC ALGORITHM 

Hierachical Clustering Algorithms (HAC)

Next we will apply hierarchical clustering methods using various distance metrics. 

```{r hac}
ev_HAC <- ev
View(ev_HAC)

distance  <- dist(ev_HAC, method = "euclidean")
distance2 <- dist(ev_HAC, method = "maximum")
distance3 <- dist(ev_HAC, method = "manhattan")
distance4 <- dist(ev_HAC, method = "canberra")
distance5 <- dist(ev_HAC, method = "binary")
distance6 <- dist(ev_HAC, method = "minkowski")

#DISPLAY THE RESULTS
HAC <- hclust(distance3, method="complete")
plot(HAC, cex=0.6, hang=-1)
rect.hclust(HAC, k =4, border=2:5)
```
## KNITTING ERROR - When I try to knit this file to HTML I get an error that says "processing file: 12_Assignment_Barletta_Alt.Rmd
Error in parse_block(g[-1], g[1], params.src) : duplicate label 'setup'
Calls: <Anonymous> ... process_file -> split_file -> lapply -> FUN -> parse_block
Execution halted"